---
title: "Proposal"
author: "Group 8"
date: "5/7/2021"
output: html_document
---

# Introduction
  Our goal is to figure out what factors contribute to the rank in which certain billionaires fall. The rank is comparing the income between billionaires and we are interested in whether age, gender, company type, location, inherited through family, or the year the company was founded, played a large factor in their rank. We are interested in the lifestyle choices that billionaires make in order to become as successful as they are today. The topic was something that interested all of us for our future lives and billionaires have always been a topic of interest because of how differently they live their lives.  
  
# Data
 
```{r message = FALSE, warning = FALSE}

library(tidyverse)

billionaires <- read_csv(here::here("data/billionaires.csv"))
glimpse(billionaires)

```
  
## Data Analysis Plan
  Our primary variable of interest is the rank of billionaires. We will be using demographics.age, demographics.gender, company.sector, location.citizenship, company.founded, and wealth.type.  
\  

### It takes some time for a person to become wealthy. For those billionaires, was it always the case that the longer their company founded the wealthier they were? In another words, is the year of foundation related to the ranking positively?  

```{r}

billionaires %>% 
  filter(company.founded != 0) %>% 
  ggplot(aes(x = company.founded,
             y = rank)) +
  geom_point() +
  facet_grid(.~year) +
  labs(x = "Year Founded",
       y = "Rankings") +
  theme(text = element_text(size = 15)) +
  theme_update()

```
  
Based on the graph of wealth rankings and year of foundation under different years, the majority of billionaires founded their companies in 1900-2000. There were many top wealth rankings came from the majority group. Therefore, it is not the case that the rank and foundation years are positively related. People can set up a company relatively late and still become top-ranking billionaires.  
\  

### The type of wealth is also very related to the rankings. People might have wealth inherited from their families or they made their own fortune. What type of wealth have the highest median rankings among other types?  

```{r}

highest_median_type <- billionaires %>% 
  filter(wealth.type != "", year == 2014) %>% 
  select(rank, wealth.type) %>% 
  mutate(wealth.type = as.factor(wealth.type)) %>% 
  group_by(wealth.type) %>% 
  summarize(Rank_Median = median(rank),
            Rank_Mean = mean(rank)) %>% 
  filter(Rank_Median == min(Rank_Median)) %>% 
  select(wealth.type) %>% 
  pull()

```
  
The type of wealth which were `r highest_median_type` has the highest ranking median, so those people might have decent positions on the wealth board.  
\  

### It is reasonable that the environment of regions will affect people's lives. Better regions may have more rich people. It is possible that the citizenship will be related to the rank.  

```{r}
counts <- billionaires %>% 
  filter(year == 2014) %>% 
  count(location.citizenship, sort=TRUE)
counts
```

```{r}
mean_median_region <- billionaires %>% 
  filter(year == 2014) %>% 
  select(location.citizenship, rank) %>%
  group_by(location.citizenship) %>% 
  summarize(mean_rank = mean(rank, na.rm = TRUE),
            median_rank = median(rank, na.rm = TRUE))

max_mean_region <- mean_median_region %>% 
  filter(mean_rank == max(mean_rank)) %>% 
  select(location.citizenship) %>% 
  pull()

max_med_region <- mean_median_region %>% 
  filter(mean_rank == max(median_rank)) %>% 
  select(location.citizenship) %>% 
  pull()
```
  
According the table above, citizenship have effect on the number of billionaires. Strong countries such as USA, Germany and China have more billionaires, but we should also consider the different amounts of populations in different regions. Moreover, `r max_mean_region` has the largest average rank and `r max_med_region` has the largest median rank. However, these regions with the largest mean and the largest median have only few billionaires.  
\  

### We also wanted to test whether gender played a role in the ranking of billionaires and also tested to what percentage of billionaires are women compared to men.  

```{r}
## selecting top 50 billionaires for 2014
billionaires <- read_csv(here::here("data/billionaires.csv"))
billionaire_2014 <- billionaires %>%
  filter(year == 2014 & rank <= 50) %>%
  rename(money_rank = "wealth.worth in billions") 


# graph top 50 billionaires to see gender comparison
ggplot(data = billionaire_2014, 
       aes(x = rank, 
           y = money_rank, 
           #size = money_rank,
           color = demographics.gender)) + 
  geom_point() + 
  labs(title = "Top 50 Billionaires in 2014", y = "wealth (billions)") + 
  theme_bw()
gender <- table(billionaires$demographics.gender)
gender
```
  
From the data on the violin graph above it seems like both female and male are pretty evenly distributed among the rankings. However, based on the larger base on the male violin, it seems like there are more male billionaires who are higher on the rankings list than females. The top 500 rankings lean more towards male than they do females. This could be explained by a number of different factors.  
\  

### We wanted to see how age played a role in the ranking of billionaires. In other words, is there a certain age, or age range where someone is more likely to be a higher ranked billionaire.  

```{r}
billionaires %>%
  filter(demographics.age>0)%>%
  ggplot(aes(x = demographics.age,
           y = rank)) +
  labs(x = "Age",
       y = "Rankings") +
  geom_point()+
  facet_grid(.~year)

billionaire_ages_2014 <- billionaires %>%
  filter(demographics.age>0, year == 2014)%>%
  select(demographics.age, rank)

median_age_2014 <- median(billionaire_ages_2014$demographics.age)
mean_age_2014 <- mean(billionaire_ages_2014$demographics.age)
```
  
From the scatterplot of the three different years, there definitely seems to a trend for the ages of the billionaires, with a majority of them appearing 
from ages 50-75. That seems to be pretty consistent as both the mean and the median are `r mean_age_2014` and `r median_age_2014` respectively. In addition, as the rank gets higher, the average age of that rank seems to increase as well.  
\  

\  

\  

# Simple Linear Regression Model on Age and Wealth
```{r}

# Select top 50 billionaires in year 2014 to do the modeling
top_50 <- billionaires %>% 
  filter(year == 2014,
         rank <= 50) %>% 
  rename(wealth = "wealth.worth in billions")

# Visual Plot
ggplot(top_50,
       aes(x = demographics.age,
           y = log(wealth))) +
  geom_point() +
  geom_smooth(method = "lm",
              se = FALSE) +
  labs(x = "Age",
       y = "Billion of Dollars",
       title = "Top 50 Billionaires") +
  theme_bw() +
  theme(text = element_text(size=16))

# Log transformation on the model
# Because the wealth variable of the top billionaires vary a lot
# By take the log of wealth, it fits the linear model better
model_age <- lm(log(wealth) ~ demographics.age,
                data = top_50)

broom::tidy(model_age)

```
  
  

### Model:
$$log(\hat{wealth_i}) = 2.992 + 0.004 * age_i$$  

### Confidence Interval:
```{r}

confint(model_age)

```  
We can obtain from the 95% confidence interval (-0.003, 0.0123) of the slope that the expected relationship between wealth and age of billionaires is very likely to be positively associated.


\  

\  

\  

## Conditions Checking:  

### Linearity
```{r echo=FALSE}

plot(model_age, 1)

```  
  
The red line is not horizontal at zero. So the linearity assumption might be is problematic.

\  

\  

\  

### Normality of residuals
```{r echo=FALSE}

plot(model_age, 2)

```  
  
Only few points fall approximately along this reference line, so the normality assumption seem to be problematic.
\  

\  

\  

### Homogeneity of residuals variance
```{r echo=FALSE}

plot(model_age, 3)

```  
  
There is an approximately horizontal line with equally spread points. So the constant variance assumption may holds.  
  
Although some of the conditions of linear regression violated in this model, but we could still get a general idea about the association between wealth and age among those billionaires.
\  

\  

\  

### Randomization Test for gender
```{r, message=FALSE, echo=FALSE}
wealth_gender_2014 <- billionaires %>% 
  filter(year == 2014) %>% 
  rename(wealth_worth = "wealth.worth in billions") %>% 
  select(demographics.gender, wealth_worth)

ggplot(wealth_gender_2014,
       aes(x = demographics.gender,
           y = wealth_worth)) +
  geom_violin() +
  labs(title = "Wealth and gender",
       x = "gender",
       y = "wealth worth in billions") +
  theme(text = element_text(size = 20))
```

Even though most of the data points for both genders fall in the pretty same region, the variance for male is large. Therefore, it is not necessary that their means are same.

# Randomization Test - 95% significant level
$$H0: \mu_1 - \mu_2 = 0$$
$$H1: \mu_1 - \mu_2 \neq 0$$
$\mu_1 = the\ mean \ of\ wealth\ worth\ for\ male$

$\mu_2 = the\ mean \ of\ wealth\ worth\ for\ female$



- Calculate the observed mean difference

- Randomly assign (sample) genders to each wealth worth

- Calculate the the sample mean for each gender

- Calculate the p-value

```{r, echo = FALSE, message=F, warning=F}
obs_means <- wealth_gender_2014 %>% 
  group_by(demographics.gender) %>% 
  summarize(mean_wealth = mean(wealth_worth)) %>% 
  select(mean_wealth) %>% 
  pull()

obs_diff <- obs_means[2] - obs_means[1]

sample_diff <- c()
set.seed(12345)

for (i in 1:1000) {
  wealth_gender_2014$stimulated_gender <-
    sample(wealth_gender_2014$demographics.gender)
  
  summary_table <- wealth_gender_2014 %>% 
    group_by(stimulated_gender) %>% 
    summarize(mean_wealth = mean(wealth_worth))
  
  sample_means <- summary_table %>% 
    select(mean_wealth) %>% 
    pull()
  
  calculated_diff <- sample_means[2] - sample_means[1]
  sample_diff <- c(sample_diff, calculated_diff)
}

hist(sample_diff)

p_value <- length(which(sample_diff <= obs_diff)) / 1000
```

__Observed difference__ = `r obs_diff`

__p-value__ = `r p_value` > 0.05

__Conclusion__: We failed to reject the null hypothesis. There is no significant evidence that there is a difference between the mean of wealth worth in billions for male and that for female in 2014.